Notes

### 2020-05-22 Notes/Notes.tex
notes updated for full counting statistics

%opening
%\title{Notes}

@@

>>>>

%opening
\title{Notes}

@@

The Lindblad operators from full counting statistics under wide-band limit is given by (arXiv:1312.3476 [quant-ph])
\begin{align}
  L_{2j}=(\sqrt{\gamma p_j}) a_j \\
  L_{2j+1}=(\sqrt{\gamma (1-p_j)} )a_j^\dagger ,
\end{align}
, where $j=(\mu,\nu)$ runs through all the level spacing between all the many-body eigen states of the system Hamiltonian for $E_\mu > E_\nu$. $p_j=\frac{1}{1+e^{-\beta (E_\mu-E_\nu)}}$. $a_j=|\nu \rangle \langle \mu |$ is the lowering operator for many-body states in the qubits system.
